Classless Java: Tuning Java Interfaces

### 2015-12-07 paper/sections/Formalization.tex
typos

\noindent
What happens if a new interface \Q@M@ extends one \Q@A@${}_i$ and one
\Q@B@${}_j$?\\*
% Nine representative cases are shown next:\\*
\noindent
\begin{tabular}{|l|l|l|l|}
\hline
\textbf{M extends} & \textbf{A1}                  & \textbf{A2} & \textbf{A3} \\ \hline
\textbf{B1}        & conservative error                        & conflict error      & conservative error       \\ \hline
\textbf{B2}        & both abstract, accepted                        & conservative error       & both abstract, accepted       \\ \hline
\textbf{B3}        & \textbf{conservative error} &conflict  error       & conservative error      \\ \hline
\end{tabular}
\\*
%We try to classify the results in the table:
\begin{itemize}
\item \textbf{conflict error} happens when the methods from both are implemented, which is also an error in most trait models.
\item \textbf{both abstract, accepted} happens when the methods from both are abstract, which is also considered correct in all
  trait models.
\item \textbf{conservative error} happens when only one method is implemented
  (leaving another one abstract), which is different from what we would expect in
  a trait model, but is coherent with the conservative idea that a method
  defined in an interface should not silently satisfy a method in another one.
\end{itemize}

>>>>

\noindent
What happens if a new interface \Q@M@ extends one \Q@A@${}_i$ and one
\Q@B@${}_j$?\\*
% Nine representative cases are shown next:\\*
\noindent
\begin{tabular}{|l|l|l|l|}
\hline
\textbf{M extends} & \textbf{A1}                  & \textbf{A2} & \textbf{A3} \\ \hline
\textbf{B1}        & conservative error                        & conflict error      & conservative error       \\ \hline
\textbf{B2}        & both abstract, accepted                        & conservative error       & both abstract, accepted       \\ \hline
\textbf{B3}        & \textbf{conservative error} &conflict  error       & conservative error      \\ \hline
\end{tabular}
\\*
%We try to classify the results in the table:
\begin{itemize}
\item \textbf{conflict error} happens when the methods from both interfaces are implemented, which is also an error in most trait models.
\item \textbf{both abstract, accepted} happens when the methods from both interfaces are abstract, which is also considered correct in all
  trait models.
\item \textbf{conservative error} happens when only one method is implemented
  (leaving another one abstract), which is different from what we would expect in
  a trait model, but is coherent with the conservative idea that a method
  defined in an interface should not silently satisfy a method in another one.
\end{itemize}

### 2015-12-07 paper/sections/Introduction.tex
revised bib and lots of small changes
typos

To formalize object interfaces, we propose Classless Java (CJ): a
FeatherweightJava-style~\cite{Igarashi01FJ} calculus, which captures the essence
of interfaces with default methods. The semantics of object interfaces
is given as a syntax-directed translation from CJ to itself. In the
resulting CJ code all object interfaces are translated into regular CJ
(and Java) interfaces with default methods. The translation is proved
to be type-preserving, ensuring that the translation does not
introduce type-errors in client code. 
%CJ's usefulness goes beyond serving as a
%calculus to formalize object interfaces. During the development
%process of CJ, we encountered a bug in the implementation of default
%methods for the Eclipse Compiler for Java (ECJ). For the program revealing the 
%bug, ECJ behaves differently from both our formalization and Oracle's 
%Java compiler.

@@

\item {\bf ClassLess Java (CJ):} A simple formal calculus that models 
the essential features of Java 8 interfaces with default methods, and 
can be used to formally define the translation of object interfaces. 
We prove several properties of the translation.

>>>>

To formalize object interfaces, we propose Classless Java (CJ): a
FeatherweightJava-style~\cite{Igarashi01FJ} calculus, which captures the essence
of interfaces with default methods. The semantics of object interfaces
is given as a syntax-directed translation from CJ to itself. In the
resulting CJ code all object interfaces are translated into regular CJ
(and Java) interfaces with default methods. The translation is proved
to be type-safe, ensuring that the translation does not
introduce type-errors in client code. 
%CJ's usefulness goes beyond serving as a
%calculus to formalize object interfaces. During the development
%process of CJ, we encountered a bug in the implementation of default
%methods for the Eclipse Compiler for Java (ECJ). For the program revealing the 
%bug, ECJ behaves differently from both our formalization and Oracle's 
%Java compiler.

@@

\item {\bf ClassLess Java (CJ):} A simple formal calculus that models 
the essential features of Java 8 interfaces with default methods, and 
can be used to formally define the translation of object interfaces. 
We prove several properties of the translation\footnote{Proofs and prototype implementation are available in
  the supplementary materials.}.
